\py{觀}{guān}
\py{自}{zì}
\py{在}{zai}
菩薩
\py{，}{}
行深
\py{般}{bō}
\py{若}{rě}
\py{波}{bō}
\py{羅}{luó}
\py{蜜}{mì}
多時
\py{，}{}
照見五蘊皆空
\py{，}{}
度一切苦厄
\py{。}{}

\py{舍}{shè}
\py{利}{lì}
\py{子}{zǐ}
\py{，}{}
色不異空
\py{，}{}
空不異色
\py{；}{}
色即是空
\py{，}{}
空即是色
\py{。}{}

受想行識
\py{，}{}
亦復如是
\py{。}{}

\py{舍}{shè}
\py{利}{lì}
\py{子}{zǐ}
\py{，}{}
是諸法空相
\py{，}{}
不生不滅
\py{，}{}
不垢不淨
\py{，}{}
不增不減
\py{。}{}

是故空中
\py{無}{wú}
色
\py{，}{}
\py{無}{wú}
受想行識
\py{。}{}

\py{無}{wú}
眼耳鼻舌身意
\py{，}{}
\py{無}{wú}
色聲香味觸法
\py{。}{}

\py{無}{wú}
眼界
\py{，}{}
乃至
\py{無}{wú}
意識界。

\py{無}{wú}
\py{無}{wú}
明
\py{，}{}
亦
\py{無}{wú}
\py{無}{wú}
明盡
\py{，}{}
乃至
\py{無}{wú}
老死
\py{，}{}
亦
\py{無}{wú}
老死盡
\py{。}{}

\py{無}{wú}
苦集滅道
\py{，}{}
\py{無}{wú}
智亦
\py{無}{wú}
得
\py{。}{}

以
\py{無}{wú}
所得故
\py{，}{}
菩提
\py{薩}{sà}
\py{埵}{duǒ}
\py{，}{}
依
\py{般}{bō}
\py{若}{rě}
\py{波}{bō}
\py{羅}{luó}
\py{蜜}{mì}
\py{多}{duō}故
\py{，}{}
心
\py{無}{wú}
\py{罣}{guà}
\py{礙}{ài}
\py{。}{}

\py{無}{wú}
\py{罣}{guà}
\py{礙}{ài}
故
\py{，}{}
\py{無}{wú}
有恐怖
\py{，}{}
遠離顛倒夢想
\py{，}{}
究竟涅
\py{槃}{pán}
\py{。}{}

三世諸佛
\py{，}{}
依
\py{般}{bō}
\py{若}{rě}
\py{波}{bō}
\py{羅}{luó}
\py{蜜}{mì}
\py{多}{duō}
故
\py{，}{}
得阿
\py{耨}{nòu}
\py{多}{duō}
羅三
\py{藐}{miǎo}
三菩提
\py{。}{}

故知
\py{般}{bō}
\py{若}{rě}
\py{波}{bō}
\py{羅}{luó}
\py{蜜}{mì}
\py{多}{duō}
\py{，}{}
是大神咒
\py{，}{}
是大明咒
\py{，}{}
是
\py{無}{wú}
上咒
\py{，}{}
是
\py{無}{wú}
等等咒
\py{，}{}
能除一切苦
\py{，}{}
真實不虛
\py{。}{}

故說
\py{般}{bō}
\py{若}{rě}
\py{波}{bō}
\py{羅}{luó}
\py{蜜}{mì}
\py{多}{duō}咒
\py{，}{}
即說咒曰
\py{：}{}

\vspace{1em}
\begin{center}
\Large
\py{揭}{jiē}
\py{諦}{dì}
\py{揭}{jiē}
\py{諦}{dì}
\py{，}{}\\
\py{波}{bō}
\py{羅}{luó}
\py{揭}{jiē}
\py{諦}{dì}
\py{，}{}\\
\py{波}{bō}
\py{羅}{luó}
\py{僧}{sēng}
\py{揭}{jiē}
\py{諦}{dì}
\py{，}{}\\
菩提薩
\py{婆}{pó}
\py{訶}{hē}
\py{。}{}
\end{center}